\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-25 NAR_DRAFT.tex
wrong citations in fig 1 fixed
citations for bioconductor packages

\begin{figure}
  \begin{center}
  \includegraphics{figures/real_signatures_only.pdf}
  \end{center}
  \caption{Tumor mutation profiles.
  In each panel, the x-axis corresponds to each of the 96 possible substitution types, and the y-axis is the proportion of total mutations of each type.
  \textbf{(A)} The observed mutation profile of an acute myeloid leukemia used in our real data analysis \cite{Griffith2015}.
  \textbf{(B)} The observed mutation profile of a breast tumor used in our real data analysis \cite{Shi2018}.
  \textbf{(C)}\&\textbf{(D)} The observed mutation profiles of two additional breast tumors \cite{Alexandrov2019}.
  \rngcomment{Label cut off in panel A. Since this figure is now all real data, we can remove "real" from each internal label.}
   }
  \label{NAR-realsigfig}
 \end{figure}

@@

\subsection{Implementation}
We have implemented the \batcave algorithm as an R package (batcaver).
The package leverages the Bioconductor packages \textrm{BSgenome}, \textrm{GenomicAlignments}, \textrm{VariantAnnotation}, and \textrm{SomaticSignatures} for fast and memory-efficient variant annotation and genomic context identification.
Reference sequences are specified as BSgenome objects, allowing efficient access to genomic context information.  \rngcomment{Add citations to all tools that have them.}

>>>>

\begin{figure}
  \begin{center}
  \includegraphics{figures/real_signatures_only.pdf}
  \end{center}
  \caption{Tumor mutation profiles.
  In each panel, the x-axis corresponds to each of the 96 possible substitution types, and the y-axis is the proportion of total mutations of each type.
  \textbf{(A)} The observed mutation profile of an acute myeloid leukemia used in our real data analysis \cite{Griffith2015}.
  \textbf{(B)} The observed mutation profile of a breast tumor used in our real data analysis \cite{Shi2018}.
  \textbf{(C)}\&\textbf{(D)} The observed mutation profiles of two additional breast tumors \cite{Alexandrov2019}.
   }
  \label{NAR-realsigfig}
 \end{figure}

@@

\subsection{Implementation}
We have implemented the \batcave algorithm as an R package (batcaver).
The package leverages the Bioconductor packages \textrm{BSgenome} \citep{Pages2019}, \textrm{GenomicAlignments} \citep{Lawrence2013}, \textrm{VariantAnnotation} \citep{Obenchain2014}, and \textrm{SomaticSignatures} \citep{Gehring2015} fast and memory-efficient variant annotation and genomic context identification.
Reference sequences are specified as BSgenome objects, allowing efficient access to genomic context information.
